---
title: "Minor Project"
author: "Rae"
date: "6 March 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

###Libraries required

```{r}
install_github("BarbaraRobson/ereefs")
install_github("dkahle/ggmap")
install_github("mdsumner/ncdf4")
```

```{r}
library(devtools)
library(ncdf4)
library(ggplot2)
library(ereefs)
library(readr)
```



###eReefs Models
*get_ereefs_profile(var_names = "Temp",location_latlon = c(), start_date = c(2016, 2, 4), end_date = c(2016, 3, 2), input_file = "menu", input_grid = NA,eta_stem = NA, squeeze = TRUE, override_positive = FALSE)*
  
```{r}
e2016_3<- get_ereefs_profile(var_names = c("temp"), location_latlon = c(-17.73,146.4), start_date = c(2016, 03, 26), end_date = c(2016, 03, 26))


janP <- get_ereefs_profile(var_names = "temp", location_latlon = c(-15, 153), start_date = c(2019, 01, 01), end_date = c(2019, 01, 31))

plot_ereefs_profile(profileObj = e2016_3, var_name = "temp", target_date = c(2016, 03, 26))

#######
sliceT <- get_ereefs_slice(var_names="temp")

plot_ereefs_slice(sliceT, var_name = "temp")

map_ereefs(var_name="temp_expose")

```


  
###Glider data  
  
*nc_open( filename, write=FALSE, readunlim=TRUE, verbose=FALSE, 
 	auto_GMT=TRUE, suppress_dimvals=FALSE )*
 	
```{r}
g2015_11csv<- read_csv("TIME_DEPTH_LAT_LON_PSAL_TEMP_CNDC_VBSC_CDOM_CPHL_DOX1_DOX2_IRRAD443_IRRAD490_IRRAD555_IRRAD670_BBP.csv")

g2015_11nc <- nc_open("MySubset_Aims_2015_11_27.nc")



ggplot(g2016_3, aes(temp, depth), ylim=rev(range(1,30))) +  geom_path() + theme_bw()

plot(  xlim = c(29, 29.8), ylim=rev(range(1,30)))
```
 	
 	
```{r}
glider <- function(x) { 
  temp <- ncvar_get(x, 'TEMP')
  depth <- ncvar_get(x, 'DEPTH')
  timeS <- ncvar_get(x, 'TIME')
  lat <- ncvar_get(x, 'LATITUDE')
  long <- ncvar_get(x, 'LONGITUDE')
  data.frame(timeS, lat, long, depth, temp)
  
}
```


```{r}

g2015_11 <- glider(nc_open("MySubset_AIMS_2015_11_27.nc"))
g2015_11 <- na.omit(g2015_11)

attach(g2015_11)
ggplot(g2015_11, aes(long, lat)) +  geom_path() + theme_bw()
ggplot(added_time, aes(temp, depth)) + scale_y_continuous(trans = "reverse") +  geom_path() + theme_bw()


time <- as.POSIXlt((g2015_11$timeS)*86400, "Australia/Brisbane", origin = as.POSIXlt("1950-01-01", "UTC"))

added_time <- cbind(g2015_11, time)

as.POSIXlt((x$time)*86400, "Australia/Brisbane", origin = as.POSIXlt("1950-01-01", "UTC"))


as.POSIXlt(15000.34, "Australia/Brisbane", origin = as.POSIXlt("1950-01-01"))

```

 	
#Comparing matching depths 
- match location = -18.59, 147.09
- match day = 2017 12 01 (I am assuming it is taking the time closest to 12 so will use glider data between 11-12pm)
- match depth = 5, 10, 15
- find the average temperature of both 

```{r}
e1201_5 <- get_ereefs_depth_specified_ts(var_names = "temp", depth = 5, start_date = c(2017, 12, 01), end_date = c(2017,12,01), location_latlon = c(-18.59,147.09), input_file = 6)

e1201_10 <- get_ereefs_depth_specified_ts(var_names = "temp", depth = 10, start_date = c(2017, 12, 01), end_date = c(2017,12,01), location_latlon = c(-18.59,147.094), input_file = 6)

e1201_15 <- get_ereefs_depth_specified_ts(var_names = "temp", depth = 15, start_date = c(2017, 12, 01), end_date = c(2017,12,01), location_latlon = c(-18.59,147.09), input_file = 6)

```


```{r}
g1711_12 <- glider(nc_open("IMOS_ANFOG_BCEOPSTUV_20171107T015221Z_SL209_FV01_timeseries_END-20171208T042436Z.nc"))

#add time and date
g1711_12$time <- as.POSIXlt((g1711_12$timeS)*86400, "Australia/Brisbane", origin = as.POSIXlt("1950-01-01", "UTC"))
g1711_12$time <- as.character(g1711_12$time)

g1711_12$date <- as.Date(g1711_12$timeS, origin = "1950-01-01")

g1711_12$date <- as.character(g1711_12$date)



# try to subset to only have 2017 12 01 @ 11 an 12 


g171201_d <- g1711_12[which(g1711_12$date == c("2017-12-01")), names(g1711_12) %in% c("timeS", "lat", "long", "depth", "temp", "time")]


  ##find the index of 11:00:00 and 12:00:00
start_time <- which(g171201_d$time == "2017-12-01 11:00:00", arr.ind = T) 
end_time <- which(g171201_d$time == "2017-12-01 12:00:00", arr.ind = T)

g171201_h <- g171201_d[c(start_time:end_time),c(1:6)]


### subset 5, 10 and 15 m 
g1201_5 <- g171201_h[which( g171201_h$depth > 4.5 & g171201_h$depth < 5.5), names(g171201_h) %in% c("lat", "long", "depth", "temp")]
g1201_5a <- mean(g1201_5$temp)
g1201_5s <- sd(g1201_5$temp)

g1201_10 <- g171201_h[which( g171201_h$depth > 9.5 & g171201_h$depth < 10.5), names(g171201_h) %in% c("lat", "long", "depth", "temp")]
g1201_10a <- mean(g1201_10$temp)
g1201_10s <- sd(g1201_10$temp)

g1201_15 <- g171201_h[which( g171201_h$depth > 14.5 & g171201_h$depth < 15.5), names(g171201_h) %in% c("lat", "long", "depth", "temp")]
g1201_15a <- mean(g1201_15$temp)
g1201_15s <- sd(g1201_15$temp)

```	
 	
###combining results from 
data: either eReefs (e) or glider (g)
depth: 5, 10, 15 
temperature
sd(for glider means)
```{r}
c1201
```

plot lat/long
```{r}

```



#comparing profiles
- match loaction
- plot of both profiles side by side 
```{r}

```



 ###Notes
 > as.date to convert teh different dates into the same format
 
 
 
#Using fuzzy verification methods tho compare eReefs and glider data
- glider trajectory as a time series
- glider temperature is averaged into model volumetric cells at discrete time intervals (these intervals match with time-step of the model = 1 hour in the case of GBR1)
- co-loacting model and glider time and space to be able to visualise temperature as a time series
- timeseries + depth and number of observation to quantitatively assess
- input: glider file with location and temperature
- output: time series file with location, glider average temperature, model temperature and model bounds


- at each time interval matching the location of glider with model and averages the temperature 
    -- I do not understand what is being averaged as the glider only goes through each location and time once. 
      --- is it averaging the temperature from that hour? But then wouldnt the number of observations used be the same as they are taken every 2 seconds from the glider? + cant really average out temperatures over different depths. 
      --- is it averaging the temperature from that hour in that location with may be several profiles 
    

#z-grid
