---
title: "single depth comparisons"
author: "Rae"
date: "13 March 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---


1. get nc glider data and convert to a workable data.frame
2. convert date and time
3. subset specific day and time (averaging an hour of glider data)
4. subset specific depths and average (subsetting +/- 0.5 m around selected depth)
5. download corresponding model temperature from eReefs (get_ereefs_depth_specific_ts())
6. combine eReef and glider temperatures 
7. plot using ggplot 
- next steps are to perfom some statistical analysis of any difference
- to see if teh step by step code i have used can be turn into a function to male it easy to change days/locations
- find out if there is a way to compute coordindates to distance (m) in R
- find out about get_ereefs_depth_specific_ts() time 
  -- at the moment assuming it is like the others and taking around midday but couldnt find this in the code
- why teh time seems to be off
 -- eg when I subset a specific date it take from 10am to 10am not midnight to midnight is it because I selected Brisbane time
 
 -- really need to refine the locations!!
 



#Glider
created thsi short fucntion to extract the variables I need from the glider nc file
```{r}
glider <- function(x) { 
  temp <- ncvar_get(x, 'TEMP')
  depth <- ncvar_get(x, 'DEPTH')
  timeS <- ncvar_get(x, 'TIME')
  lat <- ncvar_get(x, 'LATITUDE')
  long <- ncvar_get(x, 'LONGITUDE')
  data.frame(timeS, lat, long, depth, temp)
}
```

extracts wanted data
```{r}
g_gbr1711 <- glider(nc_open("IMOS_ANFOG_BCEOPSTUV_20171107T015221Z_SL209_FV01_timeseries_END-20171208T042436Z.nc"))
```

adding time and date
```{r}
g_gbr1711$time <- as.POSIXlt((g_gbr1711$timeS)*86400, origin = as.POSIXlt("1950-01-01", "UTC"))
g_gbr1711$time <- as.character(g_gbr1711$time)

g_gbr1711$date <- as.Date(g_gbr1711$timeS, origin = "1950-01-01")
g_gbr1711$date <- as.character(g_gbr1711$date)

g_gbr1711$depth_msl <- (g_gbr1711$depth*(-1)+"eta")
```

selecting the day
```{r}
g_gbr_d <- g_gbr1711[which(g_gbr1711$date == c("2017-12-01")), names(g_gbr1711) %in% c("timeS", "lat", "long", "depth", "temp", "time")]
```

selection the time
```{r}
start_time <- which(g_gbr_d$time == "2017-12-01 11:30:00") 
end_time <- which(g_gbr_d$time == "2017-12-01 12:00:00"), 

g_gbr_h<- g_gbr_d[c(start_time:end_time),c(1:6)] #make sure start_time/end_time are correct

```

```{r}
gd_5 <- g_gbr_h[which( g_gbr_h$depth > 4.5 & g_gbr_h$depth < 5.5), names(g_gbr_h) %in% c("lat", "long", "depth", "temp")]
gd_5a <- mean(gd_5$temp)
gd_5s <- sd(gd_5$temp)

gd_10 <- g_gbr_h[which( g_gbr_h$depth > 9.5 & g_gbr_h$depth < 10.5), names(g_gbr_h) %in% c("lat", "long", "depth", "temp")]
gd_10a <- mean(gd_10$temp)
gd_10s <- sd(gd_10$temp)

gd_15 <- g_gbr_h[which( g_gbr_h$depth > 14.5 & g_gbr_h$depth < 15.5), names(g_gbr_h) %in% c("lat", "long", "depth", "temp")]
gd_15a <- mean(gd_15$temp)
gd_15s <- sd(gd_15$temp)
```

find lat and long
```{r}
round(mean(g_gbr_h$lat), digits=3)
round(min(g_gbr_h$lat), digits=3)
round(max(g_gbr_h$lat), digits=3)
round(mean(g_gbr_h$long), digits=3)
round(min(g_gbr_h$long), digits=2)
round(max(g_gbr_h$long), digits=3)
```


#eReefs

at the moment have to manually input the selected dates, depth and location
```{r}

ed_5 <- get_ereefs_depth_specified_ts(var_names = "temp", depth = 5, start_date = c(2017, 12, 01), end_date = c(2017, 12, 01), location_latlon = c(-18.585, 147.090), input_file = 6)
ed_5a <- ed_5$temp

ed_10 <- get_ereefs_depth_specified_ts(var_names = "temp", depth = 10,start_date = c(2017, 12, 01), end_date = c(2017, 12, 01), location_latlon = c(-18.585, 147.090), input_file = 6)
ed_10a <- ed_10$temp

ed_15 <- get_ereefs_depth_specified_ts(var_names = "temp", depth = 15, start_date = c(2017, 12, 01), end_date = c(2017, 12, 01), location_latlon = c(-18.585, 147.090), input_file = 6)
ed_15a <- ed_15$temp

```


# Combining results from either data set

```{r}
c_temp <- c(ed_5a, ed_10a, ed_15a, gd_5a, gd_10a, gd_15a)
c_depth <- c(5, 10, 15, 5, 10, 15)
c_data <- c("eReefs","eReefs","eReefs","Glider","Glider","Glider")
c_sd <- c(0, 0, 0, gd_5s, gd_10s, gd_15s)
c171201 <- data.frame(c_temp, c_depth, c_data, c_sd)
```

#plotting
```{r}
ggplot(c171201, aes(c_temp, c_depth, colour=c_data), ) + geom_point() + geom_path() + scale_y_continuous(trans = "reverse") + theme_bw() + labs(title="Glider/eReefs Comparison 01-12-2017 GBR (-18.585, 147.090)",x="Temperature", y = "Depth below surface (m)") + geom_errorbarh(aes(xmin=c_temp-c_sd, xmax=c_temp+c_sd), height = 0.15)
```



#IMPROVEMENTS
get_ereefs_profile()
- z_grid boundaries (vertically)
- eta == adjust the depth for glider 
- spacial grid
